When the parameters are tuned in the configuration file, TaskTrackerManager is enabled. The configuration in this experiment is configured as following.
\begin{align*}
&{\bf mapred.child.java.opts = -Xmx700m}\\
&{\bf mapred.cluster.map.memory.mb = 150}\\
&{\bf mapred.cluster.reduce.memory.mb = 150}\\
&{\bf mapred.cluster.max.map.memory.mb = 200}\\
&{\bf mapred.cluster.max.reduce.memory.mb = 200}\\
&{\bf mapred.job.map.memory.mb = 150}\\
&{\bf mapred.job.reduce.memory.mb = 150}\\
&{\bf mapred.tasktracker.map.tasks.maximum = 2}\\
&{\bf mapred.tasktracker.reduce.tasks.maximum = 1}\\
\end{align*}

When we run this experiment, the map task fails due to the setting of mapred.job.map.memory.mb = 150. As we found that everytime a maptask starts, the virtual memory will directly allocate 1153683456 bytes(about 1GB), which is much larger than 150MB. And also, after we set mapred.job.map.memory.mb = 150 to 2000, which is 2GB. The task can start successfully, but the mapred.cluster.max.map.memory.mb = 200 is triggered as 1GB is larger than 200MB. TaskMemoryManagerThread will start to choose one task to kill, so the task will never start to run successfully. Then we set mapred.cluster.max.map.memory.mb to 2000, which is also 2GB. Now the task can start, but as we have mentioned in section 2.1.2, the total running virtual memory for all tasks in one task tracker should not be larger than the total memory that can be used for all the mapper and reducer. So TaskMemoryManager starts to work again to kill tasks. 
\par
Our system Memmetric can not gather virtual memory usage as in hadoop JVM metrics, so there is no such metrics to report the virtual memory usage to ganglia. When a task starts, Memmetric can only get the actual memory usage for heap and commited memory usage which is actually physical memory usage. This experiment only proves there is case that task tracker itself manage the memory usage for all the tasks running on this tracker. But we are not very clear why they use virtual memory for each task to make the judegement whether this task uses too much memory and need to be killed. 